Proposal full title \\ Proposal Acronym

### 2001-10-09 drafts/IST/PartA.tex
Call identifier
svn path=/trunk/; revision=1497
added milestones where PM means project month and delivrables, and more descriptions on project
svn path=/trunk/; revision=1498

Call identifier & \\ \hline

@@

\\ 1087/924 chars need some check and some other stuff

@@

multiple purposes, our focus will be on development hosting facilities. 
created network (for example savannah or sourceforge) ;

% 450
%COOPX
\subsection*{Milestones and expected result (max 500 characters)}
%%% HELP HELP
\section*{A4 Cost Summary}
%% will look at that later
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}

>>>>

Call identifier & IST-01-7-1B\\ \hline

@@

\\ 
%1087/924 chars need some check and some other stuff

@@

multiple purposes, our focus will be on development hosting facilities. \\

To achieve this goal, we will 
1 redesing existing hosting architectures such as Savannah and Picolibre 
  so that they may be packaged, installed and taylored easily; 
2 integrate multilanguage support to these platforms and implement support
  versions for portuguese, german, spanish, english and french;
3 define common data types and representation between the two types of
  platform with possible interaction with other platform via the CoopX project;
4 introduce functionalities to import/export informations from one site to
  another, based on this common data representation;
5 test and deploy over wide area network at least three sites in three out
	of four participating countries.
%1445/1224 chars need check and more description
\subsection*{Milestones and expected result (max 500 characters)}
PM 3: specification of new hosting architecture
PM 6: specification of common data formats
PM 9: V1 of savannah with new design 1 language version
PM12: V1 of picolibre with new design
      V2 of savannah with support for at least 2 languages and import/export
PM15: V2 of picolibre with multilingual support for at least 2 languages and
      import/export functionalities
PM18: deployment of redesigned platform in 3 countries, 
      dissemination of the project results by a Debian package.
%496/408
\section*{A4 Cost Summary}
%% will look at that later
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}
